\sysfull

### 2017-11-14 paper/compiler.tex
partial pass over compiler.  I got interrupted, but I will come back to this latter today

\sys provides compiler support for \emph{automatic task generation} that simplifies writing task-based code by automatically translating C code into a task-based executable. Doing so requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task, or are made explicit in inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime. The \sys compiler, based on LLVM, first analyzes the control-flow graph (CFG) and, using a rule-based heuristic, determines at which points to place a task boundary. After identifying where to put task boundaries, the \sys compiler transforms the imperative code into tasks, instrumenting protected memory accesses.

@@

\sys analyzes a program to determine where to put task boundaries to divide the program into tasks. A task is a single-entry, multiple-exit region of the CFG and in a correct task decomposition, no task should ever consume more energy than the device's energy buffer can store. There are several factors that determine whether tasks will execute efficiently. A task decomposition should minimize the number of variables that are accessed by multiple tasks and, consequently, must be protected by \sys's paging mechanism. Tasks should be roughly the same size, simplifying \sys's dynamic reasoning about coalescing by eliminating the need to consider variable task cost at run time. To minimize overhead introduced at task boundaries (i.e., commit), a task decomposition should maximize task size, which minimizes the frequency of task transitions.

@@

The input to the task boundary identification analysis is a standard C program (as shown in Figure~\ref{fig:compiler_overview}) and the output of \sys's analysis is the CFG, with some vertices marked as {\em task boundaries}. The \sys compiler builds the program's CFG (as shown in
Figure~\ref{fig:compiler_overview}). To simplify inter-procedural analysis, our prototype inlines all function calls into the main function in the CFG. Recursive function call cannot be handled, so the programmer has to rewrite it into a non-recursive call if there is one. The approach of always inlining function calls will introduce code duplication. If the code size is problematic, alternative approach is to make each function call a task boundary. We leave implementation of such alternative strategy as a future work.
%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%
We first describe how \sys measures each of these costs and then describe \sys's procedure for placing boundaries in the CFG.

>>>>

We studied \sys's effectiveness for systems with automatically generated task
boundaries by developing a simple compiler prototype that transforms an
arbitrary C into a program with tasks. The compiler is representative of,
although not a direct implementation of, a system that assists in writing
task-based programs by automatically inserting tasks (e.g., inspired by
Ratchet~\cite{ratchet}). 
%
Translating C code to use tasks requires identifying program points to use as
task boundaries, defining a set of task functions that begin and end at those
boundaries, ensuring that all existing control-flow paths are either contained
within a task or are made explicit with inter-task control-flow, and identifying
and instrumenting accesses to task-shared variables that need to be protected
by \sys at runtime. Our simple prototype, which is implemented using LLVM, analyzes the
control-flow graph (CFG) and uses a rule-based heuristic to determine at which
points to place a task boundary. After identifying where to put task
boundaries, the \sys compiler transforms the imperative code into tasks,
instrumenting protected memory accesses.

@@

\sys analyzes a program to determine where to put task boundaries. 
%
A task is single-entry, multiple-exit part of the CFG that our compiler excises
into a new function.  
%
There are several factors that determine whether tasks will execute
efficiently. A task decomposition should minimize the number of variables that
are accessed by multiple tasks and, consequently, must be protected by \sys's
paging mechanism. 
%
Different tasks should be approximately the same size to make reasoning about
coalescing simple by eliminating the need to consider variable run time costs. 
%
To minimize task boundary overheads (e.g., commit), a task decomposition should
maximize task size, which minimizes the frequency of task transitions.

@@

The task boundary identification analysis processes a standard C program (as
shown in Figure~\ref{fig:compiler_overview}) and produces a CFG with some
vertices marked as {\em task boundaries}. The \sys compiler builds the
program's CFG as shown in Figure~\ref{fig:compiler_overview}. In our simple reference prototype, 
we implemented inter-procedural analysis by inlining all functions called.   Recursive function call cannot be handled, so the
programmer has to rewrite it into a non-recursive call if there is one. The
approach of always inlining function calls will introduce code duplication. If
the code size is problematic, alternative approach is to make each function
call a task boundary. We leave implementation of such alternative strategy as a
future work.
%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%
We first describe how \sys measures each of these costs and then describe
\sys's procedure for placing boundaries in the CFG.
